Project-I by Group CITYNAME

### 2015-10-31 report/paper.tex
Changes to the figures

\author{
Corentin Tallec\\
Roman Shirochenko\\
EPFL \\
\texttt{corentin.tallec@epfl.ch} \\
}

@@

For our first attempt at predicting the data, we simply used the initial
features and used kFold with $k=4$ to display the evolution of the RMSE as a
function of the regularizing lambda both for the training and test data. 
The lambda we used ranged from $10^{-4}$ to
$10^3$, with 500 points. The results of the ridge regression are already
satisfactory, with an error of approximately $0.105\pm0.001$ on the training set
and $0.115\pm0.001$ on the test set, that is approximately one tenth of the
variance of the output variable.

>>>>

\author{
Roman Shirochenko\\
Corentin Tallec\\
EPFL \\
\texttt{roman.shirochenko@epfl.ch}\\
\texttt{corentin.tallec@epfl.ch} \\
}

@@

For our first attempt at predicting the data, we simply used the initial
features and used kFold with $k=4$ to display the evolution of the RMSE as a
function of the regularizing lambda both for the training and test data. 
The lambda we used ranged from $10^{-4}$ to
$10^3$, with 500 points. The results of the ridge regression are already
satisfactory, with an error of approximately $0.32\pm0.005$ on the training set
and $0.34\pm0.005$ on the test set, that is approximately one third of the
variance of the output variable.
